Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-09 mtjournal.tex
include a paragraph about syntax-based measures

\begin{itemize}
\item prior work with (partial) syntactic locality:
  \begin{itemize}
  \item Liu \& Gildea 
  \item Roark et al. Sparseval
  \item Owczarzak et al. 2007
  \end{itemize}

>>>>

\begin{itemize}
\item \sout{prior work with (partial) syntactic locality:}
  \begin{itemize}
  \item \sout{Liu \& Gildea }
  \item \sout{Roark et al. Sparseval}
  \item \sout{Owczarzak et al. 2007}
  \end{itemize}
\end{itemize}

As an alternative to these synonym- and paraphrase-based approaches,
other metrics model syntactically-local (rather than string-local)
word-sequences. \cite{liu05syntaxformteval} compared tree-local
$n$-gram precision in various configurations of constituency and
dependency trees.  The dependent-based SParseval measure
\cite{roark06:sparseval}, originally designed as a parse-quality
metric for speech, is a similar approach, in that it is an F-measure
over a decomposition of reference and hypothesis trees.
\cite{owczarzak07labelleddepseval}'s \textbf{d} and \textbf{d\_var}
measures compare LFG-derived relational tuples from reference and
hypothesis translations and report substantial improvement in
correlation with human judgment relative to BLEU and TER.

\begin{itemize}
